Predicting the effect of candidate interventions for mitigating disease spread in asymmetric-mixing metapopulations

### 2024-07-29 ms.tex
added ethnicity par stub in Intro; ready for analysis

\begin{itemize}
\item
  De Oliveira and colleagues tracked the spread of different SARS-CoV-2
  variants by village and by variant.
\item
  The goal of our model is two-fold. First, to identify parameters that
  could re-create the time series plots in Figure 1.
\item
  Second, we aim to use a parameterized model to understand how
  different intervention strategies could reduce infections among
  Reserve residents. For example, perhaps since Terena are suspected to
  travel to the
\item
  While we know a lot about transmission in the reserve, and the work of
  de Oliveira and colleagues advanced our understanding of transmission
  in the Reserve, we do not have reliable estimates of exactly how many
  cases there were per ethnicity and village. We also have only
  word-of-mouth information about the frequency of travel to the city
  for each ethnicity and location. Our model motivates the need for a
  more thorough understanding of behavior and epidemiological parameters
  in the Dourados Indigenous Reserve, and points the way towards future
  research in other Indigenous communities, and more complex situations.
  Here we only consider Indigenous mobility, but many people from the
  city travel to the reserve for commerce as well.
\end{itemize}

@@

@@

\caption{Disease reduction ($\Delta I$, y-axis) depends on the possibility of
  re-infection and the
distribution strategy to reduce travel between Dourados Reserve and city ($\Delta \gamma$, x-axis).}
\label{fig:ByReinfectionByStrategy}
\vspace{0.3em}
{\centering
  \includegraphics[width=0.95\textwidth,height=\textheight]{Figures/ResultsSketch_ByReinfectionByStrategy.pdf}

@@

\caption{Global reduction in travel to and from the city could have
Infection reduction ($\Delta I$, y-axis) for different groups could be
different as global reduction in travel to and from the city decreases
($\Delta \gamma$, x-axis).}
\label{fig:ByGroupReduction_GlobalStrategy}
\vspace{0.3em}
{\centering \includegraphics[width=0.95\textwidth,height=\textheight]{Figures/ResultsSketch_ReductionByGroup.pdf}

>>>>

\begin{itemize}
\item
  De Oliveira and colleagues tracked the spread of different SARS-CoV-2
  variants by village and by variant.
\item
  The goal of our model is two-fold. First, to identify parameters that
  could re-create the time series plots in Figure 1.
\item
  Ethnic identity is a complicated, contested concept due to coloinialism and
  various waves of oppression, repression, and genocide against Indigenous
  peoples in South America, which included various attempts at dismantling 
  and renaming pre-colonial ethnic identity~\autocite{Brandão1990}.
\item
  Second, we aim to use a parameterized model to understand how
  different intervention strategies could reduce infections among
  Reserve residents. For example, perhaps since Terena are suspected to
  travel to the
\item
  While we know a lot about transmission in the reserve, and the work of
  de Oliveira and colleagues advanced our understanding of transmission
  in the Reserve, we do not have reliable estimates of exactly how many
  cases there were per ethnicity and village. We also have only
  word-of-mouth information about the frequency of travel to the city
  for each ethnicity and location. Our model motivates the need for a
  more thorough understanding of behavior and epidemiological parameters
  in the Dourados Indigenous Reserve, and points the way towards future
  research in other Indigenous communities, and more complex situations.
  Here we only consider Indigenous mobility, but many people from the
  city travel to the reserve for commerce as well.
\end{itemize}

@@

To quantitatively compare hypothetical intervention strategies we analyze reduction
in total Once implemented,

@@

\caption{\textbf{Intervention efficacy depends on strategy and epidemiology.} Disease reduction ($\Delta I$, y-axis) depends on the possibility of
  re-infection and the
distribution strategy to reduce travel between Dourados Reserve and city ($\Delta \gamma$, x-axis).}
\label{fig:ByReinfectionByStrategy}
\vspace{0.3em}
{\centering
  \includegraphics[width=0.95\textwidth,height=\textheight]{Figures/ResultsSketch_ByReinfectionByStrategy.pdf}

@@

\caption{\textbf{Intervention efficacy will vary between groups.} 
Infection reduction ($\Delta I$, y-axis) for different groups could be
different under different mobility-reduction strategies
($\Delta \gamma$, x-axis).}
\label{fig:ByGroupReduction_GlobalStrategy}
\vspace{0.3em}
{\centering \includegraphics[width=0.95\textwidth,height=\textheight]{Figures/ResultsSketch_ReductionByGroup.pdf}
